% Acknowledgements

\pdfbookmark[1]{Acknowledgments}{Acknowledgments} % Bookmark name visible in a PDF viewer

\bigskip

%----------------------------------------------------------------------------------------

\begingroup

\let\clearpage\relax
\let\cleardoublepage\relax
\let\cleardoublepage\relax

\chapter*{Acknowledgments}

\paragraph{} I would like extend extreme gratitude to Bob, Dan, and Peter for taking in a stray grad student. Thank you to Bob for helping me transition research paths. Thank you to Dan for guidance through my very weird LUX analysis. Thank you to Peter for turning me into scientist who knows her way around a lab bench. And for teaching me a suite of skills with a razor blade, which I'm sure will raise no questions from future employers. %\\ \smallskip

Thank you to my fellow LUX/LZ grad students for being wonderful people to work with. Elizabeth, thank you for the impromptu coffee breaks. Evan, thank you for knowing the answer to literally every question of the form ``What was X in Run03?''  Brian, thank you for all the dad jokes and Mickelson trail runs. Kelsey, thank you for being an awesome officemate. Thank you to Ethan, Scott Hertel, Scott Kravitz, and Quentin for being so generous with your engineerly and postdoctorly time. You are all amazing teachers, and I have been lucky to work with you.     %\\ \smallskip

Thank you to my mom for always supporting me in my endeavor to become a physicist, and instilling me with the confidence to pursue this path in the first place. %\\ \smallskip

It's difficult to express how important support from my friends has been throughout all the years of graduate school. Jackie, Carolyn, and Michael, I could not even without you. How do? Hoodoo? Tova, I feel like you've been there through this entire test of endurance despite living in Geneva for half of it. Thank you for being my problem set buddy, for desert yoga, and for slowly realizing it was me in that wavy-arm-man costume. Heather, thank you for moving from New York into an apartment in Berkeley that was one block down the street. I am extremely lucky to call you a friend; I would not have made it though the last several years or our 10 Year Anniversary Ultramarathon without you. % \\ \smallskip

And Bradley, thank you for your unwavering support, cheerleading, and not blinking an eye despite having a front row seat to the Katayun anxiety show. You are incredible; words cannot describe.   %\\ \smallskip
 
%Thank you to Tova, Jackie, Carolyn, Mollie, Simca, Abi, and Hilary for the secret message thread that preserved my sanity during the 2016 election and continues to be a haven on those days when I need the advice of 7 badass lady physicists.
\endgroup
